\href{https://github.com/uds-datalab/PDBF}{PDBF} Documentation

### 2016-07-19 pdbf-doc.tex
corrected wrong ) -> }

\title{\href{https://github.com/uds-datalab/PDBF}{PDBF} Documentation}
\author{
 Patrick Bender \hspace{2cm} Lukas Lange \hspace{2cm} Shoaib Malik\\
  \texttt{\{s9pabend, s9lslang, s9mumali\}@stud.uni-saarland.de}
}
\date{}

@@

\noindent\textbf{Note:} To choose JSON-files as your datasource for charts, add to your SQL-FROM clause \texttt{json-files} and to your SQL-WHERE clause \texttt{filename LIKE \%What You Want\%) \\[3pt]

>>>>

\title{\href{https://github.com/uds-datalab/PDBF}{PDBF} Documentation}
\author{
 Patrick Bender \hspace{1cm} Lukas Lange \hspace{1cm} Shoaib Malik\\
  \texttt{\{s9pabend, s9lslang, s9mumali\}@stud.uni-saarland.de}
}
\date{}

@@

\noindent\textbf{Note:} To choose JSON-files as your datasource for charts, add to your SQL-FROM clause \texttt{json-files} and to your SQL-WHERE clause \texttt{filename LIKE \%What You Want\%} \\[3pt]
